\systemnamenospace: Head Orientation Based Selection\\in Physical Spaces

### 2014-08-13 doc/sui14/iteration1.tex
Grammar changes and comments

In the within-subject study, half of the participants performed {\em IR selection} first and the other half used {\em list selection} first. For each selection condition, we conducted 15 target selections by randomly choosing from all the targets. During the study, we measured the {\bf target acquisition time} for each target selection. \changes{At the beginning of each acquisition, participants were asked to stand at a fixed position approximately 10-12 feet away from the nodes. They would have to look down until the target is given. As the start to connect, they may move around if they decided it would help them select. After each task, they needed to move back to the starting position.} Afterward, participants were asked to complete a survey of primarily open-ended \changes{questions} about their experience.

@@

\changes{Most participants walked one or two steps during each task. In the survey we asked \studyquote{When you have multiple candidate targets within sight, which method for selecting between did you use?} (multiple choice), among 16 participates, X\% chose {\em adjust head so that only one candidate is signaled}, Y\% chose {\em walk closer to the candidate for a better result}, and only Z\% chose {\em tap (to enter refinement stage) and then choose between list}. \sean{will update numbers and add a few sentences here.}}

>>>>

In the within-subject study, half of the participants performed {\em IR selection} first and the other half used {\em list selection} first. For each selection condition, we conducted 15 target selections by randomly choosing from all the targets. During the study, we measured the {\bf target acquisition time} for each target selection. \changes{At the beginning of each acquisition, participants were asked to stand at a fixed position approximately 10-12 feet away from the nodes, looking down until the target is provided. As they attempt to connect, they may move around if they decided it would help them select. After each task, they were asked to move back to the starting position.} Afterward, participants were asked to complete a survey of primarily open-ended \changes{questions} about their experience.

@@

\changes{Most participants walked one or two steps during each task. In the survey we asked \studyquote{When you have multiple candidate targets within sight, which method for selecting between them did you use?} (multiple choice), among 16 participates, X\% chose {\em adjust head so that only one candidate is signaled}, Y\% chose {\em walk closer to the candidate for a better result}, and only Z\% chose {\em tap (to enter refinement stage) and then choose between list}. \sean{will update numbers and add a few sentences here.}}

### 2014-08-13 doc/sui14/iteration3.tex
Grammar changes and comments

The users had strong preferences for the new method of refinement.
\changes{Though we lack formal data to evaluate the performance of
this method, from our observation during the experiments, we found
that each trial became much easier than previous iterations. We
conducted a survey to collect qualitative feedback after the
experiment.} On a scale from 1-7, 1 being the least mental effort and
7 being the most mental effort users rated the old technique 4.25 and
the new technique 2 on average. 100\% indicated a preference for head
movement to list navigation. One user referenced the issue of naming
targets that the list necessitates, preferring the experience of
\studyquote{matching visual cues rather than numbers}.  Another
participant remarked that it \studyquote{just made more sense} and was
a \studyquote{more natural way for demonstrating intentionality}. The
users preferred the new mapping in relation to the whole environment:
\studyquote{it leveraged the spatial sense that I already had just by
using the system}. They were also delighted to avoid list navigation,
which they now called \studyquote{difficult} and \studyquote{painful}.

>>>>

The users had strong preferences for the new method of refinement.
\changes{Though we lack formal data to evaluate the performance of
this method, from our observation during the experiments, we found
that each trial became much easier than previous iterations. We
conducted a survey to collect qualitative feedback after the
experiment.} \achal{I vote changing to "Thoguh we lack... during the experiments,
we conducted..."} On a scale from 1-7, 1 being the least mental effort and
7 being the most mental effort users rated the old technique 4.25 and
the new technique 2 on average. 100\% indicated a preference for head
movement to list navigation. One user referenced the issue of naming
targets that the list necessitates, preferring the experience of
\studyquote{matching visual cues rather than numbers}.  Another
participant remarked that it \studyquote{just made more sense} and was
a \studyquote{more natural way for demonstrating intentionality}. The
users preferred the new mapping in relation to the whole environment:
\studyquote{it leveraged the spatial sense that I already had just by
using the system}. They were also delighted to avoid list navigation,
which they now called \studyquote{difficult} and \studyquote{painful}.
